---
title: "Coursera Presentation"
author: "Gergely"
date: "2023-02-10"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide

Some content

***
New slide without title

## My Title

### A top level subheading

#### A second level subheading

## Formatting Text

Plain text

*italicized text*

**bold text**

`for (i %in% 1:10)`

## New Slide for R Code

```{r comment = "", echo=TRUE, eval=TRUE}
head(mtcars)
```

## New Slide for Plot

```{r fig.align='center',fig.cap='My Awesome Figure'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

1. Item a
2. Item b

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Publish in Github

If master is renamed in github:

git branch -m master <BRANCH>
git fetch origin
git branch -u origin/<BRANCH> <BRANCH>
git remote set-head origin -a